Download, Compile and Link OpenBLAS Library with R

### 2021-04-06 README.Rmd
:art: Update logo and website
Update logo (logo with transparent background) and pkgdown.

```{r, fig.align='center', echo=FALSE, out.width=219}
knitr::include_graphics("https://raw.githubusercontent.com/prdm0/ropenblas/master/logo.png")
```

<!-- <img src="https://raw.githubusercontent.com/prdm0/ropenblas/master/logo.png" height="270" width="250" align="right" /> -->

>>>>

<!-- ```{r, fig.align='center', echo=FALSE, out.width=219} -->
<!-- knitr::include_graphics("https://raw.githubusercontent.com/prdm0/ropenblas/master/logo.png") -->
<!-- ``` -->

<img src="logo.png" height="230" width="200" align="right" />
